Powering Hidden Markov Model by Generative Models

### 2019-08-13 manuscript/main.tex
add convg

%\def\year{2020}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai20}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{graphicx}  % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
%\nocopyright
%PDF Info Is REQUIRED.
% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
 \pdfinfo{/Title gm_hmm
} %Leave this	
\newcommand{\citet}[1]{\citeauthor{#1} \shortcite{#1}}
\newcommand{\citep}{\cite}
\newcommand{\citealp}[1]{\citeauthor{#1} \citeyear{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Problem Statement}

@@

\subsection{Learning of GenHMM}

@@

\textcolor{red}{expand to neural network here}By substituting \eqref{eq:changel-variable} and \eqref{eq:cat-jacobian} into \eqref{eq:obj-q-gen-mix}, we have loss function for neural networks as
\begin{align}\label{eq:obj-q-gen-mix}
  &\Qq(\bm{\Theta}; \bm{H}^{\mathrm{old}}) \nonumber \\
  =& \frac{1}{R}\hspace{-3pt}\sum_{r=1}^{R}\hspace{-3pt} \sum_{t=1}^{{T}^{r}-1}\hspace{-3pt} \sum_{\smtr{s}{t}{r}=1}^{|\Ss|} \hspace{-3pt} \sum_{\smtr{\kappa}{t}{r}=1}^{K}p(\smtr{s}{t}{r}| \ubmr{x}{r}; \bm{H}^{\mathrm{old}})p(\smtr{\kappa}{t}{r}|\smtr{s}{t}{r}, \ubmr{x}{r}; \bm{H}^{\mathrm{old}}) \nonumber\\
&\left[ \log\, p_{\smtr{s}{t}{r}, \smtr{\kappa}{t}{r}}(\bm{f}_{\smtr{s}{t}{r}, \smtr{\kappa}{t}{r}}(\bmtr{x}{t}{r})) + \sum_{l=1}^{L}\log\,| \det (\nabla{\bm{f}_{s,\kappa}^{[l]}})|\right]
\end{align}

@@

Since $\bm{A}_{i, j}  = p(\smtr{s}{t+1}{r}=j|\smtr{s}{t}{r}=i; {A})$ where $A_{i, j}$ is the element of transition matrix $A$, the solution to problem:
\begin{align}\label{eq:update-transition-prob}
  \bm{A} = &\uargmax{\bm{A}} \Qq(\bm{A}; \bm{H}^{\mathrm{old}}), \nonumber \\
  \mathrm{s.t.} &\hspace{0.2cm} \bm{A} \cdot \bm{1} = \bm{1} \nonumber \\
                          &  \bm{A}^{\intercal} \cdot \bm{1} = \bm{1} \nonumber \\
                          & \bm{A}_{i,j} \geq 0.
\end{align}
is
\begin{equation}
  \bm{A}_{i,j} = \frac{\bar{\xi}_{i,j}}{\sum_{k = 1}^{|\Ss|} \bar{\xi}_{i,k}},
\end{equation}
where
\begin{equation}
  \bar{\xi}_{i,j} = \sum_{r= 1}^{R} \sum_{t= 1}^{T^{(r)}-1}{p(\smtr{s}{t}{r}=i, \smtr{s}{t+1}{r}=j| \ubmr{x}{r}; \bm{H}^{\mathrm{old}})}
\end{equation}

\subsection{Algorithm of GenHMM}
Algorithm here:
things to talk:
\begin{itemize}
\item separate optimization of different sets of parameters
\item batch optimization optimization
\item not going to optimal for $\bm{\Phi}$, leaving to convergence analysis in next section
\end{itemize}

@@

\begin{algorithm}[H]
  \caption{Meta algorithm for HMM powered by Generative Models (GMHMM)}
  \begin{algorithmic}[1]
    \STATE {\bfseries Input:}{
      Building $\bm{H}^{\mathrm{old}}, \bm{H} \in \Hh$ gives: \\
      $\bm{H}^{\mathrm{old}} = \{\Ss, \bm{q}^{\mathrm{old}}, A^{\mathrm{old}}, p(\bm{x}|s; \bm{\Phi}^{\mathrm{old}})\}$, $\bm{H} = \{\Ss, \bm{q}, A, p(\bm{x}|s; \bm{\Phi})\}$
    }, \\
    \STATE Initialize $\bm{H}$
    \STATE $\bm{H}^{\mathrm{old}} \gets \bm{H}$
    \FOR { $\bm{H}$ not converge}
    \STATE Sample a batch of data $\left\{ \ubmr{x}{r} \right\}_{r=1}^{R_b}$ from the dataset $\hat{p}(\ubm{x})$
    \STATE Compute $p(\smtr{s}{t}{r} | \ubmr{x}{r}; \bm{H}^{\mathrm{old}})$, $p(\smtr{s}{t}{r}, \smtr{s}{t+1}{r}| \ubmr{x}{r}; \bm{H}^{\mathrm{old}})$ by forward/backward algorithm;
    \STATE $\bm{q} \gets \uargmin{\bm{q}}\, \Qq(\bm{q}; \bm{H}^{\mathrm{old}})$ by \eqref{eq:update-initial-state-prob};
    \STATE $\bm{A} \gets \uargmin{\bm{A}}\Qq(\bm{A}; \bm{H}^{\mathrm{old}})$ by \eqref{eq:update-transition-prob};
    \STATE $\bm{\Phi} \gets \uargmin{\bm{\Phi}}\Qq(\bm{\Phi}; \bm{H}^{\mathrm{old}})$ by calling Algorithm~\ref{algo:opt-Phi-GenHMM} or \ref{algo:opt-Phi-LatHMM};
    \STATE $\bm{H}^{\mathrm{old}} \gets \bm{H}$

@@

\begin{algorithm}[H]
  \caption{M-step w.r.t. $\bm{\Phi}$ powered by GenMM}\label{algo:opt-Phi-GenHMM}
  \begin{algorithmic}[1]
    \STATE {\bfseries Input:}
    Latent mixture distribution: $\Nn\left(\bm{z}; \bm{0}, \mathrm{diag}(\bm{1})\right)$, $\forall \, s \in \Ss, \kappa = 1, 2, \cdots, K$;\\
    Empirical distribution $\hat{p}(\bm{x})$ of dataset; \\
    \STATE Set a total number of epochs $T$ of training as stop criterion. A learning rate $\eta$.
    \FOR {epoch $t < T$}
    \STATE Sample a batch of data $\left\{ \ubmr{x}{r} \right\}_{r=1}^{R_b}$ from dataset $P_d(\ubm{x})$

    \STATE Compute $p(\smtr{s}{t}{r}, \smtr{\kappa}{t}{r}| \ubmr{x}{r}; \bm{H}^{\mathrm{old}})$  by Forward/backward and \eqref{eq:kappa-posterior}.
    %     = \frac{\pi_k \Nn\left(f(X); \bm{\mu}_k^{t},\bm{\sigma}_k^{t}\right)}{\sum_{k=1}^K\; \pi_k\Nn\left(f(X); \bm{\mu}_k^{t},\bm{\sigma}_k^{t}\right) }, \forall \left\{ x^{(i)}\right\}_{i=1}^{n_b}$
    % \Comment{Calculate posterior \autoref{eq-posterior-gamma}}
    \STATE Compute loss ${\Qq}\left({\bm{\Phi}}, {\bm{H}}^{\mathrm{old}}\right)$ in \eqref{eq:obj-q-gen-mix}

    \STATE $\partial{\bm{\th}_s} \gets  \nabla_{\bm{\theta}} -
    \frac{1}{R_{b}}{\Qq}\left({\bm{\Phi}},{\bm{H}}^{\mathrm{old}}\right)$
    % \Comment{E-step}
    % \STATE $\partial{g_k} \gets \nabla_{\th_k}\widetilde{\Qq}\left(\left\{ \th_k
    %   \right\}_{k=1}^{K};\left\{ \th_k^t\right\}_{k=1}^{K}\right)$,
    % $\forall \th_k \in\left\{ \th_k\right\}_{k=1}^{K}$
    \STATE $\bm{\th}_s \gets \bm{\th}_s - \eta \cdot \partial{\bm{\theta}_s}$, $\forall s \in \Ss$
    \ENDFOR

    \STATE Update $\pi_{s, \kappa}, \forall, s\in \Ss, \kappa= 1, 2, \cdots, K$, according to \eqref{eq:mix-latent-parameter-solution}

    \STATE Assemble $\bm{\Phi} = \left\{  \bm{\Phi}_s| s \in \Ss\right\}$ for $\bm{\Phi}_s = \left\{ \bm{\theta}_{s, \kappa}, \bm{\mu}_{{s},{\kappa}}, \bm{C}_{{s},{\kappa}}| \kappa = 1, 2, \cdots, K \right\}$.

  \end{algorithmic}
\end{algorithm}

\section{Convergence Analysis}

\section{On Implementation of acoustic signal}
test citing \cite{2018arXiv180703039K}

>>>>

% \def\year{2020}\relax
% File: formatting-instruction.tex
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai20}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{graphicx}  % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
% \nocopyright
% PDF Info Is REQUIRED.
% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
\pdfinfo{/Title gm_hmm
} %Leave this	
\newcommand{\citet}[1]{\citeauthor{#1} \shortcite{#1}}
\newcommand{\citep}{\cite}
\newcommand{\citealp}[1]{\citeauthor{#1} \citeyear{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Learning in EM framework}

@@

\subsection{Learning of GenHMM}\label{subsec:optmGenHMM}

@@

By substituting \eqref{eq:changel-variable} and \eqref{eq:cat-jacobian} into \eqref{eq:obj-q-gen-mix}, we have loss function for neural networks as
\begin{align}\label{eq:obj-q-gen-mix}
  &\Qq(\bm{\Theta}; \bm{H}^{\mathrm{old}}) \nonumber \\
  =& \frac{1}{R}\hspace{-3pt}\sum_{r=1}^{R}\hspace{-3pt} \sum_{t=1}^{{T}^{r}-1}\hspace{-3pt} \sum_{\smtr{s}{t}{r}=1}^{|\Ss|} \hspace{-3pt} \sum_{\smtr{\kappa}{t}{r}=1}^{K}p(\smtr{s}{t}{r}| \ubmr{x}{r}; \bm{H}^{\mathrm{old}})p(\smtr{\kappa}{t}{r}|\smtr{s}{t}{r}, \ubmr{x}{r}; \bm{H}^{\mathrm{old}}) \nonumber\\
  &\left[ \log\, p_{\smtr{s}{t}{r}, \smtr{\kappa}{t}{r}}(\bm{f}_{\smtr{s}{t}{r}, \smtr{\kappa}{t}{r}}(\bmtr{x}{t}{r})) + \sum_{l=1}^{L}\log\,| \det (\nabla{\bm{f}_{s,\kappa}^{[l]}})|\right]
\end{align}

@@

Since $\bm{A}_{i, j}  = p(\smtr{s}{t+1}{r}=j|\smtr{s}{t}{r}=i; {A})$ where $A_{i, j}$ is the element of transition matrix $A$, the solution to problem:
\begin{align}\label{eq:update-transition-prob}
  \bm{A} = &\uargmax{\bm{A}} \Qq(\bm{A}; \bm{H}^{\mathrm{old}}), \nonumber \\
  \mathrm{s.t.} &\hspace{0.2cm} \bm{A} \cdot \bm{1} = \bm{1} \nonumber \\
           &  \bm{A}^{\intercal} \cdot \bm{1} = \bm{1} \nonumber \\
           & \bm{A}_{i,j} \geq 0.
\end{align}
is
\begin{equation}
  \bm{A}_{i,j} = \frac{\bar{\xi}_{i,j}}{\sum_{k = 1}^{|\Ss|} \bar{\xi}_{i,k}},
\end{equation}
where
\begin{equation}\label{eq:update-transition-solt}
  \bar{\xi}_{i,j} = \sum_{r= 1}^{R} \sum_{t= 1}^{T^{(r)}-1}{p(\smtr{s}{t}{r}=i, \smtr{s}{t+1}{r}=j| \ubmr{x}{r}; \bm{H}^{\mathrm{old}})}
\end{equation}

\subsection{Algorithm of GenHMM}
We goal is to minimize the KL divergence $KL(\hat{p}(\ubm{x})\| p(\ubm{x};\bm{H}))$ or maximizing$\sum_{r=1}^{R}\log\,p(\ubmr{x}{r}; \bm{H})$. The 
Algorithm here:
things to talk:
\begin{itemize}
\item separate optimization of different sets of parameters
\item batch optimization optimization
\item not going to optimal for $\bm{\Phi}$, leaving to convergence analysis in next section
\end{itemize}

@@

\begin{algorithm}[H]
  \caption{Learning of GenHMM}
  \begin{algorithmic}[1]
    \STATE {\bfseries Input:}{
      Building $\bm{H}^{\mathrm{old}}, \bm{H} \in \Hh$ gives: \\
      $\bm{H}^{\mathrm{old}} = \{\Ss, \bm{q}^{\mathrm{old}}, A^{\mathrm{old}}, p(\bm{x}|s; \bm{\Phi}^{\mathrm{old}})\}$, $\bm{H} = \{\Ss, \bm{q}, A, p(\bm{x}|s; \bm{\Phi})\}$\\
    Empirical distribution $\hat{p}(\bm{x})$ of dataset;} \\
    \STATE Initialize $\bm{H}$
    \STATE $\bm{H}^{\mathrm{old}} \gets \bm{H}$
    \STATE Set learning rate $\eta$, neural network optimization epochs $T$ per EM step.
    \FOR { $\bm{H}$ not converge}
        \FOR {epoch $t < T$}
    \STATE Sample a batch of data $\left\{ \ubmr{x}{r} \right\}_{r=1}^{R_b}$ from dataset $\hat{p}(\ubm{x})$

    \STATE Compute posterior $p(\smtr{s}{t}{r}, \smtr{\kappa}{t}{r}| \ubmr{x}{r}; \bm{H}^{\mathrm{old}})$  
    \STATE Formulate loss ${\Qq}\left({\bm{\Theta}}, {\bm{H}}^{\mathrm{old}}\right)$ in \eqref{eq:obj-q-gen-mix}

    \STATE $\partial{\bm{\Theta}} \gets  \nabla_{\bm{\Theta}} {\Qq}\left({\bm{\Theta}},{\bm{H}}^{\mathrm{old}}\right)$
    \STATE $\bm{\Theta} \gets \bm{\Theta} + \eta \cdot \partial{\bm{\theta}_s}$
    \ENDFOR
    \STATE $\bm{q} \gets \uargmax{\bm{q}}\, \Qq(\bm{q}; \bm{H}^{\mathrm{old}})$ by \eqref{eq:update-initial-state-prob};
    \STATE $\bm{A} \gets \uargmax{\bm{A}}\Qq(\bm{A}; \bm{H}^{\mathrm{old}})$ by \eqref{eq:update-transition-prob};
    \STATE $\bm{\Pi} \gets \uargmax{\bm{\Pi}}\Qq(\bm{\Phi}; \bm{H}^{\mathrm{old}})$ by \eqref{eq:update-transition-solt};
    \STATE $\bm{H}^{\mathrm{old}} \gets \bm{H}$

@@

\subsection{Convergence Analysis}
\begin{prop}
  Assume that parameters of GenHMM are in a compact set. Further assume that $\Qq(\bm{\Theta}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}) \geq \Qq(\bm{\Theta}^{\mathrm{old}}; \bm{H}^{\mathrm{old}})$, then we always have $KL(\hat{p}(\ubm{x})\| p(\ubm{x};\bm{H}^{\mathrm{new}})) \geq KL(\hat{p}(\ubm{x})\| p(\ubm{x};\bm{H}^{\mathrm{old}}))$, and GenHMM converges.
\end{prop}

\begin{proof}
  We begin with the comparison of log-likelihood evaluated under $\bm{H}^{\mathrm{old}}$ and $\bm{H}^{\mathrm{old}}$. The log-likelihood of dataset given by $\hat{p}(\ubm{x})$ can be reformulated as
  \begin{align*}
    &\EE_{\hat{p}(\ubm{x})}\left[ \log\,p(\ubm{x};\bm{H}^{\mathrm{new}}) \right] \nonumber \\
    =& \EE_{\hat{p}(\ubm{x}),p(\ubm{s},\ubm{\kappa}| \ubm{x}; \bm{H}^{\mathrm{old}})}\left[ \log\,\frac{p(\ubm{x}, \ubm{s}, \ubm{\kappa}; \bm{H}^{\mathrm{new}})}{p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{old}})}\right] \nonumber \\
    &+ \EE_{\hat{p}(\ubm{x})}\left[ KL(p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{old}})\|p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{new}})) \right],
  \end{align*}
  where the first term on the right hand side of equality can be further written as
  \begin{align*}
    &\EE_{\hat{p}(\ubm{x}),p(\ubm{s},\ubm{\kappa}| \ubm{x}; \bm{H}^{\mathrm{old}})}\left[ \log\,\frac{p(\ubm{x}, \ubm{s}, \ubm{\kappa}; \bm{H}^{\mathrm{new}})}{p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{old}})}\right] \nonumber \\
    = &\Qq(\bm{H}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}) + \EE_{\hat{p}(\ubm{x}),p(\ubm{s},\ubm{\kappa}| \ubm{x}; \bm{H}^{\mathrm{old}})}\left[p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{old}})\right].
  \end{align*}
  According to subsection~\ref{subsec:optmGenHMM}, the subproblem solutions gives
  \begin{align*}
    \Qq(\bm{q}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}) &\geq \Qq(\bm{q}^{\mathrm{old}}; \bm{H}^{\mathrm{old}}),\nonumber \\
    \Qq(\bm{A}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}) &\geq \Qq(\bm{A}^{\mathrm{old}}; \bm{H}^{\mathrm{old}}),\nonumber \\
    \Qq(\bm{\Pi}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}) &\geq \Qq(\bm{\Pi}^{\mathrm{old}}; \bm{H}^{\mathrm{old}}).
  \end{align*}
  For the learning w.r.t. neural network parameter set $\bm{\Theta}$, as long as the lose function does not decrease during EM iterations, i.e. $\Qq(\bm{\Theta}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}) \geq \Qq(\bm{\Theta}^{\mathrm{old}}; \bm{H}^{\mathrm{old}})$, we would have
  \begin{equation*}
    \Qq(\bm{H}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}) \geq \Qq(\bm{H}^{\mathrm{old}}; \bm{H}^{\mathrm{old}}),
  \end{equation*}
  since
  \begin{align*}
    \Qq(\bm{H}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}) = &\Qq(\bm{q}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}) + \Qq(\bm{A}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}) \nonumber \\
    &+ \Qq(\bm{\Pi}^{\mathrm{new}}; \bm{H}^{\mathrm{old}})
    + \Qq(\bm{\Theta}^{\mathrm{new}}; \bm{H}^{\mathrm{old}}).
  \end{align*}
  Therefore we have the inequality 
  \begin{align*}
    &\EE_{\hat{p}(\ubm{x}),p(\ubm{s},\ubm{\kappa}| \ubm{x}; \bm{H}^{\mathrm{old}})}\left[ \log\,\frac{p(\ubm{x}, \ubm{s}, \ubm{\kappa}; \bm{H}^{\mathrm{new}})}{p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{old}})}\right] \nonumber \\
    \geq &\EE_{\hat{p}(\ubm{x}),p(\ubm{s},\ubm{\kappa}| \ubm{x}; \bm{H}^{\mathrm{old}})}\left[ \log\,\frac{p(\ubm{x}, \ubm{s}, \ubm{\kappa}; \bm{H}^{\mathrm{old}})}{p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{old}})}\right].
  \end{align*}
  Due to the fact that $KL(p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{old}})\|p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{old}}))=0$, we have
  \begin{align*}
      &\EE_{\hat{p}(\ubm{x})}\left[ \log\,p(\ubm{x};\bm{H}^{\mathrm{new}}) \right] \nonumber \\
    \geq & \EE_{\hat{p}(\ubm{x}),p(\ubm{s},\ubm{\kappa}| \ubm{x}; \bm{H}^{\mathrm{old}})}\left[ \log\,\frac{p(\ubm{x}, \ubm{s}, \ubm{\kappa}; \bm{H}^{\mathrm{old}})}{p(\ubm{s}, \ubm{\kappa}|\ubm{x}; \bm{H}^{\mathrm{old}})}\right] \nonumber \\
    = & \EE_{\hat{p}(\ubm{x})}\left[ \log\,p(\ubm{x};\bm{H}^{\mathrm{old}}) \right].
  \end{align*}
  Therefore
  \begin{align*}
    KL(\hat{p}(\ubm{x})\|p(\ubm{x};\bm{H}^{\mathrm{new}})) = &\EE_{\hat{p}(\ubm{x})}\left[ \log\,\frac{\hat{p}(\ubm{x})}{p(\ubm{x};\bm{H}^{\mathrm{new}})} \right] \nonumber \\
    \leq &\EE_{\hat{p}(\ubm{x})}\left[ \log\,\frac{\hat{p}(\ubm{x})}{p(\ubm{x};\bm{H}^{\mathrm{old}})} \right] \\
    = & KL(\hat{p}(\ubm{x})\|p(\ubm{x};\bm{H}^{\mathrm{old}})).
    \end{align*}
  Since KL divergence is non-negative and thus lower bounded, GenHMM will converge.
\end{proof}

\section{Experiments}
test citing \cite{2018arXiv180703039K}
